---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# changepoint.geo 

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/changepoint.geo )](https://CRAN.R-project.org/package=changepoint.geo )
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/changepoint.geo?color=blue)](https://r-pkg.org/pkg/changepoint.geo)
[![R-CMD-check](https://github.com/grundy95/changepoint.geo/workflows/R-CMD-check/badge.svg)](https://github.com/grundy95/changepoint.geo/actions)
[![codecov](https://codecov.io/gh/grundy95/changepoint.geo/branch/master/graph/badge.svg?token=97a3PkoGw6)](https://codecov.io/gh/grundy95/changepoint.geo)
<!-- badges: end -->

The goal of changepoint.geo is to implement the high-dimensional changepoint detection method GeomCP described in [Grundy et al. (2020)](https://link.springer.com/article/10.1007/s11222-020-09940-y). This method allows for the detection of changes in mean and variance in high-dimensional time series. The main function is `geomcp()`.

## Installation

You can install the released version of changepoint.geo from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("changepoint.geo ")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("grundy95/changepoint.geo")
```
## Example

This is a basic example which shows the main functionality of the package:

```{r example}
library(changepoint.geo )
set.seed(1)
X <- rbind(matrix(rnorm(100*50),ncol=50),matrix(rnorm(100*50,0,2),ncol=50))
ans <- geomcp(X)
summary(ans)
plot(ans)
```


<!-- You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>. -->


